### 2017-12-11 submission/manuscript.Rmd
complete error result section -- more finished

***Per Base Error Rate is Dependent on both Taq and Cycle Number Used:***
Differences by HiFi Taq in the median average per base error varied without a clear pattern across sub-sampling depth []. Generally, the highest values were for the Kappa HiFI Taq [Figure 3A]. Sub-sampling depth seems to have little effect on this rate with both 5000 and 10000 sub-sampled sequences showing similar results [Figure 3B & C]. Generally, there were small differences between the various HiFi Taq at lower cycle number but larger differences at higher cycle number [Figure 3B & C]. Platinum HiFi Taq consistently had the highes median average per base error rate while Phusion and Accuprime had the lowest [Figure 3B & C]. These differences though were realtively small between the different HiFi Taq [Figure 3]. The total seqeunces with at least one error matched the median average per base error except for the Accuprime HiFi Taq [Figure S1]. Although it had the lowest per base error rate it had either the largest or second largest number of sequences with at least one error regardless of cycle number of sub-sampling depth [Figure S1]. Investigation of whether there were Taq dependent effects on base subsitution found that there was no clear bias and this was indpendent of sub sampling depth [Figure S2-S4]. Further, the variation in subsitution error seems to reduce as the sequencing depth increases [Figure S2-S4].

>>>>

***Sequence Error is Dependent on both Taq and Cycle Number Used:***
Differences by HiFi Taq in the median average per base error varied without a clear pattern across sub-sampling depth [Table S5]. Generally, the highest values were for the Kappa HiFI Taq [Figure 3A]. Sub-sampling depth seems to have little effect on this rate with both 5000 and 10000 sub-sampled sequences showing similar results [Figure 3B-C]. There were small differences between the various HiFi Taq at lower cycle number but larger differences at higher cycle number with Platinum having large differences between all other HiFi Taq [Figure 3B-C and Table S6].

The total seqeunces with at least one error had multiple differences at different cycle numbers and sub-sampling depth driven by large differences in Accuprime^TM^ and Platinum versus the other HiFi Taq tested [Figure S1 & Table S7 & S8]. Although Accuprime^TM^ had the lowest per base error rate it had either the largest or second largest number of sequences with at least one error regardless of cycle number or sub-sampling depth [Figure S1]. Investigation of whether there were Taq dependent effects on base subsitution found that there was no clear bias and this was indpendent of sub-sampling depth [Figure S2-S4]. Further, the variation in subsitution error seems to reduce as the sub-sampling depth increases [Figure S2-S4].

### 2017-12-11 submission/manuscript.tex
complete error result section -- more finished

\textbf{\emph{Per Base Error Rate is Dependent on both Taq and Cycle
Number Used:}} Differences by HiFi Taq in the median average per base
error varied without a clear pattern across sub-sampling depth {[}{]}.
Generally, the highest values were for the Kappa HiFI Taq {[}Figure
3A{]}. Sub-sampling depth seems to have little effect on this rate with
both 5000 and 10000 sub-sampled sequences showing similar results
{[}Figure 3B \& C{]}. Generally, there were small differences between
the various HiFi Taq at lower cycle number but larger differences at
higher cycle number {[}Figure 3B \& C{]}. Platinum HiFi Taq consistently
had the highes median average per base error rate while Phusion and
Accuprime had the lowest {[}Figure 3B \& C{]}. These differences though
were realtively small between the different HiFi Taq {[}Figure 3{]}. The
total seqeunces with at least one error matched the median average per
base error except for the Accuprime HiFi Taq {[}Figure S1{]}. Although
it had the lowest per base error rate it had either the largest or
second largest number of sequences with at least one error regardless of
cycle number of sub-sampling depth {[}Figure S1{]}. Investigation of
whether there were Taq dependent effects on base subsitution found that
there was no clear bias and this was indpendent of sub sampling depth
{[}Figure S2-S4{]}. Further, the variation in subsitution error seems to
reduce as the sequencing depth increases {[}Figure S2-S4{]}.

>>>>

\textbf{\emph{Sequence Error is Dependent on both Taq and Cycle Number
Used:}} Differences by HiFi Taq in the median average per base error
varied without a clear pattern across sub-sampling depth {[}Table S5{]}.
Generally, the highest values were for the Kappa HiFI Taq {[}Figure
3A{]}. Sub-sampling depth seems to have little effect on this rate with
both 5000 and 10000 sub-sampled sequences showing similar results
{[}Figure 3B-C{]}. There were small differences between the various HiFi
Taq at lower cycle number but larger differences at higher cycle number
with Platinum having large differences between all other HiFi Taq
{[}Figure 3B-C and Table S6{]}.

The total seqeunces with at least one error had multiple differences at
different cycle numbers and sub-sampling depth driven by large
differences in Accuprime\textsuperscript{TM} and Platinum versus the
other HiFi Taq tested {[}Figure S1 \& Table S7 \& S8{]}. Although
Accuprime\textsuperscript{TM} had the lowest per base error rate it had
either the largest or second largest number of sequences with at least
one error regardless of cycle number or sub-sampling depth {[}Figure
S1{]}. Investigation of whether there were Taq dependent effects on base
subsitution found that there was no clear bias and this was indpendent
of sub-sampling depth {[}Figure S2-S4{]}. Further, the variation in
subsitution error seems to reduce as the sub-sampling depth increases
{[}Figure S2-S4{]}.
